Preprocessing and exploration of the narwhal data for the analysis with smoothSDE

### 2024-04-06 R/preprocessing/data_preprocessing.Rmd
Update preprocessing

```{r read raw data}
# Set the path to the directory containing the data
par_dir=dirname(dirname(getwd())) #parent directory 
narwhal_data_path <- file.path(par_dir,"Data", "Narwhals")

@@

```{r trajectories map}

@@

```{r compute nearest shore points}

>>>>

```{r read raw data,cache=TRUE}
# Set the path to the directory containing the data
par_dir=dirname(dirname(getwd())) #parent directory 
narwhal_data_path <- file.path(par_dir,"Data", "Narwhals")

@@

```{r trajectories map,cache=TRUE}

@@

```{r compute nearest shore points,cache=TRUE}
